Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-03-15 paper.tex
misc

\begin{lstlisting}
def nd[T,S](ts: Set[T], acc: S, f: (T, S, S=>S) => S, g: S => S): S = {
  if (ts.isEmpty) g(acc)
  else f(ts.head, acc, (vss: S) => nd(ts.tail, vss, f, g))
}

>>>>

\begin{lstlisting}
def nd[T,S](ts: Set[T], acc: S, f: (T, S, S => S) => S, g: S => S): S = {
  if (ts.isEmpty) g(acc)
  else f(ts.head, acc, (vss: S) => nd(ts.tail, vss, f, g))
}
